---
title: "Project Data Set"
author: "Qi Yu"
date: "`r format(Sys.Date(), '%b %d %Y')`"
output:
  html_document:
    df_print: paged
---

```{r, echo = F}
knitr::opts_chunk$set(
  echo = F,
  message = F
)
```


## Introduction
[Pima Indians Diabetes Database](https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database?resource=download) would be the dataset for my R Markdown project. The dataset was collected by the National Instite of Diabetes and Digestive and Kidney Disease. The objective of this dataset is to diagnostically predict whether or not the patients have diabetes based on several diagnostic measurements. The dataset consists of one outcome variable and 8 medical predictor variables including the number of pregnancies the patient has had, their age, BMI and so on. The outcome variable in binary. In this report, I'd like to conduct an exploratory analysis of this dataset.

## Load Dataset
First, we load the data.
```{r}
#| echo = T
here::i_am("QiYu_ProjectReport.Rmd")
load("output/data.Rdata")
```


```{r}
library(tidyr)
library(dplyr)
library(knitr)
library(ggplot2)
library(patchwork)
library(ggpubr)
```

```{r, include = F}
#data |> glimpse()
data |> glimpse()
```


## Check Dataset

Second, we check the data.

Table 1 and table 2 shows the contents of the dataset. As shown in figure 1 and 2, there are eight medical predictor variables and one dummy outcome variable representing whether or not the patients have diabetes. As shown, among eight predictor variables, "BMI" and "Diabetes Pedigree Function" are continuous variables, while other six varibles are integer variable.
```{r}
table1
```

```{r}
table2
```


## Exploratory Analysis
Third, we conduct exploratory data analysis.

Figure 1 and figure 2 show predictors and outcome histogram plots and predictors box plots. We can find that "BMI" , "Glucose" and "Blood pressure" are normal-like distributed; "Skin thickness" and "Insulin" seem to be normal, but both variables have plenty of "0" value records which are potentially outliers; "Diabetes Pedigree function" and "Age" are right skewed. 

Based on this exploratory analysis, an outlier analysis is recommended before conducting further analysis. 

```{r}
#| fig.align = "center",
#| out.width = "600px"
load("output/boxplots.RData")
load("output/histagram.RData")

his_plots <- ggarrange(hist_skin, hist_pedigree, hist_bmi, hist_insulin, hist_age, hist_blood, hist_glucose, count_outcome,
          labels = c("A", "B", "C", "D", "E", "F", "G","H"), 
          ncol = 3, nrow = 3)

box_plots <- ggarrange(box_skin, box_pedigree, box_bmi, box_insulin, box_age, box_blood, box_glucose,
          labels = c("A", "B", "C", "D", "E", "F", "G","H"), 
          ncol = 3, nrow = 3)

annotate_figure(his_plots,
                top = text_grob("Figure 1: Predictors and Outcome Histogram Plots", color = "black", face = "bold", size = 14))

annotate_figure(box_plots,
                top = text_grob("Figure 2: Predictors Box Plots", color = "black", face = "bold", size = 14))
```

```{r}
#| fig.align = "center",
#| out.width = "600px"
```


